---
title: "Vectorized_image_filter_intermediate_R"
author: "Eyvind Liljegren"
date: "`r Sys.Date()`"
output: html_document
---
# Markdown file to simplify reading the code and testing it

available at: 

https://github.com/eyvindj/VectorizedColorFilter.git

run the first chunk to load package (if not already loaded)
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(VectorizedColorFilter)

```

## Filter with grayscale function and the optional twocolor filter

### Usage:filter_twocolor <- function(your_image, cutoff = 97,         color1="pink",color2="blue")
 
`your_image` Requires input in the format of standard image format (eg. .jpg .png) or an image object.

`cutoff` Default: 97, (range 0-255) RGB with numerical values.

`color1` Default: "pink", Any color in RGB, either numerical or hexadecimal and all standard colors in  within "".

`color2` Default: "blue", Any color in RGB, either numerical or hexadecimal and all standard colors in  within "".


"
```{r, include= TRUE, echo = FALSE }
filter_twocolor <- function(your_image, cutoff = 97, color1="pink",color2="blue") {

  if (is.character(your_image) && file.exists(your_image)) {

    img <- tryCatch({                # Try to read the file as an image
      magick::image_read(your_image)
    }, error = function(e) {
      stop("The provided path is not a valid image file.") #error with message
    })                                                       # Input is already an image object
  } else if (inherits(your_image, "magick-image")) {        # tries to read as an image and brings its class
    img <- your_image
  } else {
    stop("Input must be a valid image file or a magick image object.")  # if not image or filepath
  }


  bitmap <- magick::image_data(img) #read your file file from your chosen filepath (preferably in project directory)

  color_1 <- c(col2rgb(color1))
  color_2 <- c(col2rgb(color2))
  #print(color_1)
  #print(color_2)
  # Convert to grayscale
  grayscale <- round(
    0.299 * as.numeric(bitmap[1, , ]) +
      0.587 * as.numeric(bitmap[2, , ]) +
      0.114 * as.numeric(bitmap[3, , ])
  )

  # Create an empty filtered bitmap
  filtered_bitmap <- bitmap

  # Apply the cutoff condition
  above_cutoff <- grayscale > cutoff
  filtered_bitmap[1, , ][above_cutoff] <- as.raw(color_1[1])   # R
  filtered_bitmap[2, , ][above_cutoff] <- as.raw(color_1[2])    # G
  filtered_bitmap[3, , ][above_cutoff] <- as.raw(color_1[3])   # B (Color_1)

  below_cutoff <- !above_cutoff
  filtered_bitmap[1, , ][below_cutoff] <- as.raw(color_2[1])    # R
  filtered_bitmap[2, , ][below_cutoff] <- as.raw(color_2[2])   # G
  filtered_bitmap[3, , ][below_cutoff] <- as.raw(color_2[3])   # B (Color_2)


  filtered_image <- magick::image_read(filtered_bitmap)
  #print(as.raw(color_2))
  return(filtered_image)
}



```

## Test files

Code with example file to test the filter function

```{r Test filter,include=TRUE, echo=TRUE}


testimage <- system.file("extdata", "test.jpg", package = "VectorizedColorFilter")
testimage2 <- system.file("extdata", "test2.jpg", package = "VectorizedColorFilter")

testimage <- magick::image_read(testimage)
testimage2 <- magick::image_read(testimage2)


gray1 <- filter_grayscale(testimage)
gray2 <- filter_grayscale(testimage2)


twocolor1 <- filter_twocolor(testimage, color1="yellow", color2="lightblue")
twocolor2 <- filter_twocolor(testimage2, color1="yellow", color2="lightblue")

par(mfrow = c(2, 3),    # 2 rows, 3 columns
    mar = c(1, 1, 1, 1), # Margins around each plot (bottom, left, top, right)
    oma = c(0, 0, 0, 0)) # Outer margin (optional)


# Plot the images
plot(testimage)
plot(gray1)
plot(twocolor1)
plot(testimage2)
plot(gray2)
plot(twocolor2)
```


